\documentclass{article}
\usepackage[letterpaper, left=2cm,top=2cm,right=2cm,bottom=2cm]{geometry}
\usepackage{setspace}
%\singlespacing 
%\onehalfspacing  
%\doublespacing 
\setstretch{1.2}
\pdfpagewidth 8.5in
\pdfpageheight 11.0in
\brokenpenalty=10000
\usepackage[utf8]{inputenc}

\title{What is the best book for?}
\author{Behzad~Nouri,~{\small PhD ECE}}
\date{June 2019}

\begin{document}

\maketitle
\tableofcontents
\newpage
%---------------------------------------------------------------
%  Circuit Theory
%---------------------------------------------------------------
\section{Circuit Theory}
These two books will build up our foundations very well.
\begin{enumerate}
\item \textbf{Network Analysis}
    \\by: Valkenburg
    \\[6pt]M. E. Van Valkenburg, Network analysis, 3d ed. Englewood Cliffs, N.J: Prentice-Hall, 1974.
    %
    \item \textbf{Engineering Circuit Analysis}
    \\by: Steven M. Durbin, Jack E. Kemmerly, William H. Hayt
    \\[6pt]W. Hayt, J. Kemmerly, J. Phillips, and S. Durbin, Engineering Circuit Analysis, 8th ed. McGraw-Hill, 2012.
    \\[6pt]\textbf{Note:}~This has plenty of examples helping a clear and easy understanding.
    %
    \item \textbf{Fundamentals of Electric Circuits}
    \\by: Charles K. Alexander, Matthew N. O. Sadiku
    \\[6pt]C. K. Alexander and M. N. O. Sadiku, Fundamentals of electric circuits - (4ed), 4th ed. Boston: McGraw-Hill, 2009.
    \\[6pt]\textbf{Note:} It has (1) many solved examples with detailed solution steps (2) chapters that introduce students to PSpice and MatLab (3) Section on the Fourier Series, the Fourier Transform and the Laplace Transform.

    \item \textbf{Fundamentals of Circuit Theory}\\
    by: D.~Chattopadhyay and P.~C.~Rakshit
    %
    \item \textbf{Basic Circuit Analysis Book}\\
    by: J.~David Irwin and R.~Mark~Nelims
    %
    \item\textbf{Classical Circuit Theory}\\
    by: Omar Wing
    %
\end{enumerate}

\newpage
%---------------------------------------------------------------
% Electromagnetic (Theory \& Numerical)
%---------------------------------------------------------------
\section{Electromagnetic-Theory (\& Numerical)}
%
\begin{enumerate}
\item \textbf{Introduction to Electrodynamics}\\
(3rd Edition, ISBN:9780138053260)\\
by:David J. Griffiths
%
\item \textbf{Electricity and magnetism}\\
(3rd Edition, ISBN:9781107014022, 2013)\\
by: Edward M. Purcell and David J Morin
%
\item \textbf{Fundamentals of Applied Electromagnetics}\\
(4th Edition, 2017)
by: Fawwaz T. Ulaby,Umberto Ravaioli
%
\item \textbf{Engineering Electromagnetics}\\
(ISBN: 0805344233)\\
by: Umran S. Inan and Aziz Inan
%
\item \textbf{Engineering Electromagnetics}\\
(ISBN: 3319078054, 2015)\\
by: Nathan Ida
%
\item \textbf{Engineering Electromagnetics}\\
(6th Edition, ISBN: 0072304243, 2000)\\
by: William H, Hayt and John A.Buck
%
\item \textbf{Fundamentals of Electromagnetics with Engineering Applications}\\
(ISBN: 0470105755, 2006)\\
by: Stuart M. Wentworth
%
\item \textbf{Electromagnetics with Applications}\\
(5th Edition, ISBN: 0072899697, 1999)\\
by: John Daniel Kraus, Daniel A. Fleisch
\end{enumerate}


\newpage
%---------------------------------------------------------------
% Statistics and Probability
%---------------------------------------------------------------
\section{Probability Theory}
%
\begin{enumerate}
%
\item{%
    \textbf{A first course in probability},\\[2pt]
     Ross, Sheldon M.\\
     $9^{th}$ Ed., 2014, ISBN: 978-0-321-79477-2,
     }
%
\item{%
    \textbf{Introduction to probability models},\\[2pt]
     Ross, Sheldon M.\\
     $10^{th}$ Ed., 2010, ISBN: 978-0-12-375686-2,
     }
%
\item{%
	\textbf{Probability \& statistics for engineers \& scientists},\\[2pt]
	Walpole, Ronald E and Myers, Raymond H and Myers, Sharon L and Ye, Keying,\\
	$9^{th}$ Ed., 2017, ISBN: 978-1-292-16141-9,
	}
%
\item{%
	\textbf{Probability and Random Processes},\\[2pt]
	Grimmett, Geoffrey R. and Stirzaker David R.\\
	$3^{rd}$ Ed., 2001, ISBN: 0198572220,
	}
%
\item{%
	\textbf{One thousand exercises in probability (Solution Manual of Probability and Random Processes)},\\[2pt]
	Grimmett, Geoffrey R. and Stirzaker David R.\\
	2001, ISBN: 978-0-19-857221-3,
	}	
%
\item{%
    \textbf{Probability: theory and examples},\\[2pt]
     Durrett, Richard\\
     $4^{th}$ Ed., 2010, ISBN: 978-0-521-76539-8,
     }
%
\item{%
    \textbf{Intuitive probability and random processes using MATLAB},\\[2pt]
     Kay, Steven M.\\
     $1^{st}$ Ed., 2006, ISBN: 978-0-387-24157-9,
     } 
%	
\end{enumerate}


\end{document}
